Technical Paper Proposal: \\ Placement Algorithms for Heterogenous FPGAs

### 2024-09-13 docs/proposal/proposal.tex
more editing

    The compilation stages mainly consists of lexing, parsing, and instruction optimization.
    While these stages are complex from a systems standpoint, they are, mathematically, trivial.
    The EDA stages on the other hand are deeply mathematically complex. 
    First, the FPGA engineer creates and describes a digital design using a hardware description language (HDL) like Verilog or VHDL.     
    Then the engineer submits the design entry to an EDA like Vivado or Quartus to perform three stages of automated design. 
    These are mainly: synthesis, placement, and routing. 
    All three are NP-hard problems.

>>>>

    The compilation stages mainly consists of lexing, parsing, and optimization.
    The optimization stage is where most of the complexity occurs as it deals with NP-hard problems.
    The compiler at this stage must optimize the ordering of the machine instructions to maximize pipelining and register allocation.
    While the search space for the best possible machine code is massive, it is typically constrained to the size of the CPU instruction set and architecture which are fixed.
    Furthermore, compiler makers have developed highly efficient heuristics to approximate the best machine code within an acceptable runtime.

    On the other hand, the EDA stages consist mainly of synthesis, placement, and routing.
    All three are NP-hard optimization problems with massive search spaces with massive search spaces.
    Even with heuristics and approximations to circumvent NP-hardness, the size of their search spaces make the EDA runtimes less than acceptable.

    In a typical FPGA design flow, the engineer creates and describes a digital design using a hardware description language (HDL) like Verilog or VHDL.     
    Then, the FPGA engineer verifies the design by creating a testbench that wraps around the design and feeds the design input signals and observes the output signals.
    % The formal verification process is an art of its own and is so matured that companies will often separate their engineers into two departments - one focusing on design and the other on verification.
    Then the engineer submits the design entry to an EDA like Vivado or Quartus to perform the three stages of automated design.
